Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
fin todo order

Increasing land cover resolution resulted in decreased availability of foraging habitat,
a rare habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). <!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again. I think this should be reordered so it's easier to follow. -->
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.

>>>>

Increasing land cover resolution resulted in decreased availability of foraging habitat,
a rare habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). 
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
